%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Ph.D. in Information and Communication Technology} % Degree
    {\href{https://www.unipd.it/}{University of Padova (UNIPD)}} % Institution
    {Padova, Italy} % Location
    {Oct. 2019 - Oct. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Thesis}: ML-driven Environment Sensing with millimeter-Wave radars}
        \item {Granted 3-year full scholarship as a part of \href{https://www.b5g-mints.eu/}{\textbf{MINTS}} research group in \href{https://cordis.europa.eu/project/id/861222}{MSCA ITN H2020 (Grant no: 861222)}}
        \item {Managed \href{https://b5g-mints.eu/blog/}{\textit{\textbf{blog duties}}} of 15 PhD students (scheduling, reviewing and publishing) and supervised a MSc. student through their thesis period}
      \end{cvitems}
    }
  
  \cventry
    {M.Sc. in Applied Mathematics and Computer Science} % Degree
    {\href{https://www.emu.edu.tr/en}{Eastern Mediterranean University (EMU)}} % Institution
    {Famagusta, Cyprus} % Location
    {Sep. 2017 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\href{http://i-rep.emu.edu.tr:8080/xmlui/handle/11129/5291}{\textbf{Thesis}}: Person-Dependant and Independant Facial Emotion Recognition on eNTERFACE, SAVEE and RML datasets using SVM and NN \href{https://link.springer.com/article/10.1007/s11760-020-01830-0}{\textbf{[paper]}}}
        \item {Awarded a Research Assistant Software Engineering position, developed internal features for university infrastructure with .NET, MySQL, NodeJS}
        \item {\textbf{Main Courses}: Distributed and Parallel Programming, Cryptography and Network Security, Artificial Intelligence, Decision Making}
      \end{cvitems}
    }

  \cventry
    {B.S. in Computer Engineering} % Degree
    {\href{https://www.bilkent.edu.tr/}{Bilkent University}} % Institution
    {Ankara, Turkey} % Location
    {Sep. 2012 - Jul. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Graduation Project}: NetWord: A social network based on text-based games developed with Android Studio and Google Firebase \href{https://bitbucket.org/enverbashirov/networdclient}{\textbf{[code]}}}
        \item {\textbf{Main Courses}: Digital Design, Computer Organization, Operating Systems, Artificial Intelligence, Image Analysis, Computer Graphics}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
