%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {AI \& Team Lead} % Job title
    {\href{https://www.hekanize.com}{Hekanize}} % Organization
    {Padova, Italy} % Location
    {Dec. 2024 - Present} % Date(s)
    {
      \begin{cvitems}
        \item {Joined as one of the first engineers; shaped the tech team and product direction for a SaaS CRM platform}
        \item {Built and led a team of 8 developers and coordinated 2 external supplier teams}
        \item {Stabilized a microservice-based architecture, significantly improving uptime and scalability}
        \item {Designed and deployed production-ready AI modules using LangChain, LangGraph, FastAPI, PyTorch, and TensorFlow}
        \item {Rebuilt AWS infrastructure with Terraform (S3, EC2, ECS, Lambda, IAM, CloudFront, etc.) and optimized for cost and reliability}
        \item {Oversaw CI/CD pipelines and debugging across multiple stacks (C\#, Java, Python, PHP)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer · Computer Vision Engineer} % Job title
    {\href{https://www.geoinference.com/en/homeeng/}{GeoInference}} % Organization
    {Padova (Remote), Italy} % Location
    {Oct. 2024 - Nov. 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Developed a client-server segmentation service (REST API, Flask, Python) to detect distinct objects in containers} 
        \item {Built a computer vision pipeline for sawblade defect detection using OpenCV}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Machine Learning Engineer (Research)} % Job title
    {\href{https://b5g-mints.eu/}{MINTS}} % Organization
    {Padova, Italy} % Location
    {Mar. 2020 - Mar. 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Developed radar-based deep learning models (CNN, RNN, Autoencoders, YOLOv3) for human tracking using PyTorch}
        \item {Implemented distributed, multi-threaded edge computing systems with Python sockets and TCP/IP}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Machine Learning Engineer} % Job title
    {Nokia Bell Labs} % Organization
    {Espoo, Finland} % Location
    {May 2022 - Aug. 2022} % Date(s)
    {
      \begin{cvitems}
        \item {Built WiFi signal peak detection pipeline with decision trees, pandas, numpy, and scikit-learn}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Machine Learning Engineer} % Job title
    {IMDEA Networks} % Organization
    {Madrid, Spain} % Location
    {Jan. 2021 - Jun. 2021} % Date(s)
    {
      \begin{cvitems}
        \item {Designed TensorFlow-based models for human activity recognition and implemented signal denoising algorithms}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Eastern Mediterranean University (EMU)} % Organization
    {Famagusta, Cyprus} % Location
    {Sep. 2018 - Jul. 2019} % Date(s)
    {
      \begin{cvitems}
        \item {Contributed to the university’s internal systems (C\#, .NET, MySQL, NodeJS, TypeScript, AngularJS)}
        \item {Improved front-end for the official university webpage using .NET, AngularJS, HTML5, and CSS3}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
